---
title: "Final Project"
author: "Sai Ananthula"
date: "2023-04-08"
output:
  html_document: default
  pdf_document: default
---


## Loading statements for needed packages
```{r echo=TRUE}
library(tidyverse)
library(naniar)
library(simputation)
library(readxl)
library(lubridate)
library(corrplot)
library(vtable)
```



## Extract data from Excel sheets into 2 tibbles
```{r}
Raw_Data <- read_excel("RawData.xlsx", sheet = "Raw-Data")
Calendar <- read_excel("RawData.xlsx", sheet = "Calendar")
```


## Calculate number of missing values and then the number of rows in the overall data set
```{r}
n_miss(Raw_Data)
nrow(Raw_Data)
```


## Standardize column names
```{r}

Raw_Data<- Raw_Data %>%
  rename(Ship_Date = `Ship Date`, PO_Download_Date = `PO Download Date`, Ship_Date = `Ship Date`, Receipt_Date = `Receipt Date`, Ship_Mode = `Ship Mode`)

```


## Drop rows with missing data and then recalculate number of rows in data set
```{r}
Raw_Data <- Raw_Data %>%
  drop_na(Ship_Date)

nrow(Raw_Data)
```

## Function to add quarter and year to Raw Data set
```{r}

quarter_year <- function(data_master, data_secondary)
{
  data_master <- data_master %>%
    mutate(Quarter = "",Year = 0)
  
  for(i in 1:nrow(data_master)) 
  {
    
      for(j in 1:nrow(data_secondary))
      {
          if(data_master[i,"Receipt_Date"] >= data_secondary[j,"Start_Date"] &      
             data_master[i,"Receipt_Date"] <= data_secondary[j,"End_date"] ) 
            {
              
              data_master[i,"Quarter"] <- data_master[i,"Quarter"] %>%
                       mutate(Quarter = as.character(data_secondary[j,"Quarter"]))
              
              data_master[i,"Year"] <- data_master[i,"Year"] %>%
                       mutate(Year = as.numeric(data_secondary[j,"Year"]))
            }
            
            
      }
    

  }
  
  return(data_master)
  
}

Raw_Data_QY <- quarter_year(Raw_Data,Calendar)

```


## Calculate Transit/Manufacturing columns
```{r}
Raw_Data_QY <- Raw_Data_QY %>%
  mutate(In_Transit_Lead_Time = difftime(Receipt_Date, Ship_Date,units = "days" )) %>%
  mutate(Manufacturing_Lead_Time = round(difftime(Ship_Date, PO_Download_Date,units = "days" )))
```
## Remove rows with lead time values less than 0
```{r}
Raw_Data_QY <- Raw_Data_QY %>%
  filter(In_Transit_Lead_Time > 0 & Manufacturing_Lead_Time > 0)
```

## Calculate number of rows after removal
```{r}

nrow(Raw_Data_QY)
```

## Build new tibble with all columns converted to numeric
```{r}
Raw_Data_Numeric <- Raw_Data_QY %>% 
  mutate(LOB = as.numeric(as.factor(LOB))) %>%
  mutate(Origin = as.numeric(as.factor(Origin))) %>%
  mutate(Ship_Mode = as.numeric(as.factor(Ship_Mode))) %>%
  mutate(Quarter = as.numeric(as.factor(Quarter))) %>%
  mutate(PO_Download_Date = as.numeric(PO_Download_Date)) %>%
  mutate(Ship_Date = as.numeric(Ship_Date)) %>%
  mutate(Receipt_Date = as.numeric(Receipt_Date)) %>%
  mutate(In_Transit_Lead_Time = as.numeric(In_Transit_Lead_Time)) %>%
  mutate(Manufacturing_Lead_Time = as.numeric(Manufacturing_Lead_Time))
  
```


## Remove Year
```{r}
Raw_Data_Numeric <- Raw_Data_Numeric %>%
  select(-Year)
```



## Calculate correlation Table
```{r}
cor(Raw_Data_Numeric)
```

## Generate Correlation Plots
```{r}
corrplot(cor(Raw_Data_Numeric), method = "color", diag = FALSE, type = "lower")
corrplot(cor(Raw_Data_Numeric), method = "number", diag = FALSE, type = "lower")
```

## Generate Summary Statistics
```{r}
st(Raw_Data_QY, vars = c("LOB","Origin","Quarter","Ship_Mode","In_Transit_Lead_Time","Manufacturing_Lead_Time") )
```

## Convert Lead Times To Numeric
```{r}
Raw_Data_Numeric_2 <- Raw_Data_QY %>% 
  mutate(In_Transit_Lead_Time = as.numeric(In_Transit_Lead_Time)) %>%
  mutate(Manufacturing_Lead_Time = as.numeric(Manufacturing_Lead_Time))
  
```

## Graphs Comparing Predictor Variables Against Transit Lead Time
```{r}

ggplot(Raw_Data_Numeric_2, aes(Origin,In_Transit_Lead_Time)) +
 stat_summary(geom =  "col", fun = mean) 

ggplot(Raw_Data_Numeric_2, aes(Ship_Mode,In_Transit_Lead_Time, fill = )) +
 stat_summary(geom =  "col", fun = mean)


ggplot(Raw_Data_Numeric_2, aes(Origin, In_Transit_Lead_Time, color = Ship_Mode)) +
  geom_point()
```



